A performance assessment of evolutionary algorithms in volunteer computing environments

### 2016-10-30 EvoPar2017/paper.Rnw
Lo siento, borré la historia...
Anonymizes authors closes #128

\title{A performance assessment of evolutionary algorithms in a
  volunteer computing system}

\author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
  Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}

\institute{Dept. of Computer Architecture and Technology, University
of Granada, Spain \and
Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

@@

This work has been supported in part by TIN2014-56494-C4-3-P (Spanish
Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio
2015 UGR). We are also grateful to {\tt @otisdriftwood} for his help
gathering users for the new experiments.

>>>>

\title{A performance assessment of evolutionary algorithms in
  volunteer computing environments}

% \author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
%   Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}

% \institute{Dept. of Computer Architecture and Technology, University
% of Granada, Spain \and
% Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

\author{A.U. Thor \and A. N. Otherauthor \and Just A. Nother \inst{1}
  \and Jet A. Nother \inst{2}}

\institute{Invisible University, Frantzia \and
Institute of Higher Studies, Zootropa}

@@

% This work has been supported in part by TIN2014-56494-C4-3-P (Spanish
% Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio
% 2015 UGR). We are also grateful to {\tt @otisdriftwood} for his help
% gathering users for the new experiments.

Several projects\\
Taking\\
This\\
Much\\
Space\\

### 2016-10-30 EvoPar2017/paper.tex
Anonymizes authors closes #128

\author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
  Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}

\institute{Dept. of Computer Architecture and Technology, University
of Granada, Spain \and
Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

>>>>

% \author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
%   Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}

% \institute{Dept. of Computer Architecture and Technology, University
% of Granada, Spain \and
% Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

\author{A.U. Thor \and A. N. Otherauthor \and Just A. Nother \inst{1}
  \and Jet A. Nother \inst{2}}

\institute{Invisible University, Frantzia \and
Institute of Higher Studies, Zootropa}
